\documentclass[preprint,12pt]{elsarticle}
%\documentclass[preprint,review,12pt]{elsarticle}
%\documentclass[final,1p,times]{elsarticle}

\usepackage{preamble}
\usepackage{array}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{subcaption}
\usepackage{float}
%\usepackage{lineno}
%\linenumbers
%\usepackage{background}
%\backgroundsetup{contents=Confidential}

\setlength{\arrayrulewidth}{0.1mm}

\journal{Journal XXXXXXXX}

\begin{document}

\tableofcontents

\newpage

\begin{frontmatter}

\title{BIM-FM interoperability: integrating IFC models' visualization and existing FM platforms}

\author[inst1]{Andressa Oliveira}
\author[inst1]{José Granja}
\author[inst2]{Pedro Machado}
\author[inst3]{Ali Motamedi}
\author[inst1]{Miguel Azenha}

\affiliation[inst1]
            {organization={University of Minho, ISISE, ARISE, Department of Civil Engineering},
            city={Guimarães},
            country={Portugal}}

\affiliation[inst2]
            {organization={Matosinhos City Council},
            city={Matosinhos},
            country={Portugal}}

\affiliation[inst3]
            {organization={Université du Québec à Montreal, École de Technologie Supérieure},
            city={Newcastle},
            country={United Kingdom}}
        
\begin{abstract}
The adoption of Building Information Modelling (BIM) in the operational phase of buildings is still restricted. One of the factors hindering adoption of the methodology is the lack of BIM capabilities in Facility Management (FM) platforms, such as three-dimensional visualisation of the buildings to be managed. This article presents a solution designed in collaboration with the Matosinhos City Council in Portugal to enable the management of its assets using the BIM methodology. The purpose of the solution is to integrate the current management platform used by the council (Infraspeak) with three-dimensional visualisation resources, and to allow the consultation and manipulation of operational data directly and integrated with this visualisation. The use of information models (BIM models) that follow the IFC (Industry Foundation Classes) scheme has been considered for asset visualisation. In this context, an integrated and customised web platform was developed using the IFCjs library to manipulate, investigate and visualise IFC files. In addition, the platform allows direct connection to the Infraspeak database via its Application Programming Interface (API). This article details the development process of the integration platform, its key components and its interoperability with Infraspeak. The solution developed is an innovative approach to the current limitations in operations management and supports the wider adoption of BIM for the FM area.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Facility Management (FM) \sep Building Information Modelling (BIM) \sep Interoperability \sep Integration
\end{keyword}

\end{frontmatter}

%This command determines from where the lies will start to be numbered
%\linenumbers

\input{1.introduction}
%\pagebreak
\input{2.methodology}
%\pagebreak
\input{3.framework}
%\pagebreak
\input{4.conclusion}
%\pagebreak
\input{5.acknowledgements}
%\pagebreak

%\appendix
%\input{appendix}

\bibliographystyle{elsarticle-num} 
\bibliography{library}
 
\end{document}
\endinput
